\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2022-03-26 doc/USER_MANUAL/02_getting_started.tex

The SPECFEM3D Cartesian software package relies on the SCOTCH library
to partition meshes created with CUBIT. METIS \citep{KaKu98a,KaKu98c,KaKu98b}
can also be used instead of SCOTCH if you prefer, by editing file
src/decompose\_mesh/decompose\_mesh.F90 and uncommenting the flag
USE\_METIS\_INSTEAD\_OF\_SCOTCH. You will also then need to install
and compile Metis version 4.0 (do {*}NOT{*} install Metis version
5.0, which has incompatible function calls) and edit \texttt{src/decompose\_mesh/Makefile.in}
and uncomment the METIS link flag in that file before running \texttt{configure}.\\

The SCOTCH library \citep{PeRo96} provides efficient static mapping,
graph and mesh partitioning routines. SCOTCH is a free software package
developed by Fran\c{c}ois Pellegrini et al. from LaBRI and INRIA in Bordeaux,
France, downloadable from the web page \url{https://gforge.inria.fr/projects/scotch/}.
In case no SCOTCH libraries can be found on the system, the configuration
will bundle the version provided with the source code for compilation.
The path to an existing SCOTCH installation can to be set explicitly
with the option \texttt{-{}-with-scotch-dir}. Just as an example:
\begin{verbatim}
  ./configure FC=ifort MPIFC=mpif90 --with-scotch-dir=/opt/scotch
\end{verbatim}
\noindent
If you use the Intel ifort compiler to compile the code, we recommend
that you use the Intel icc C compiler to compile Scotch, i.e., use:
\begin{verbatim}
  ./configure CC=icc FC=ifort MPIFC=mpif90
\end{verbatim}

>>>>

The SPECFEM3D Cartesian software package relies on the SCOTCH library
to partition meshes created with CUBIT. METIS \citep{KaKu98a,KaKu98c,KaKu98b}
can also be used instead of SCOTCH if you prefer, by changing the parameter
\texttt{PARTITIONING\_TYPE} in the \texttt{Par\_file}. You will also then need to install
and compile Metis version 4.0 (do {*}NOT{*} install Metis version
5.0, which has incompatible function calls) and edit \texttt{Makefile.in}
and uncomment the METIS link flag in that file before running \texttt{configure}.\\

The SCOTCH library \citep{PeRo96} provides efficient static mapping,
graph and mesh partitioning routines. SCOTCH is a free software package
developed by Fran\c{c}ois Pellegrini et al. from LaBRI and INRIA in Bordeaux,
France, downloadable from the web page \url{https://gitlab.inria.fr/scotch/scotch}.
In case no SCOTCH libraries can be found on the system, the configuration
will bundle the version provided with the source code for compilation.
The path to an existing SCOTCH installation can to be set explicitly
with the option \texttt{-{}-with-scotch-dir}. Just as an example:
\begin{verbatim}
  ./configure FC=ifort MPIFC=mpif90 --with-scotch-dir=/opt/scotch
\end{verbatim}
\noindent
If you use the Intel ifort compiler to compile the code, we recommend
that you use the Intel icc C compiler to compile Scotch, i.e., use:
\begin{verbatim}
  ./configure CC=icc FC=ifort MPIFC=mpif90
\end{verbatim}

### 2022-03-26 doc/USER_MANUAL/04_creating_databases.tex

The present version of SPECFEM can handle fully saturated porous simulations.
(Christina Morency implemented Biot's equation.
However, the code cannot calculate partially saturated cases in its state.
Christina Morency is presently working on a dual porosity, dual permeability formulation, type Pride and Berryman, for an other project, but it will not be available for some time.)
The way we prescribe material property for porous material in SPECFEM3D is as follow.
We use a file \texttt{nummaterial\_poroelastic\_file}, which is located in the directory \texttt{MESH/}. The line format is as follow:
{\small \begin{verbatim}
  rhos rhof phi c kxx kxy kxz kyy kyz kzz Ks Kf Kfr etaf mufr
\end{verbatim}}
\begin{description}
\item where\\
\texttt{rho\_s} = solid density,\\
\texttt{rho\_f} = fluid density,\\
\texttt{phi} = porosity,\\
\texttt{tort} = tortuosity,\\
\texttt{kxx} = xx component of permeability tensor,\\
\texttt{kxy} = xy,yx components of permeability tensor,\\
\texttt{kyy} = yy component of permeability tensor,\\
\texttt{kxz} = xz,zx components of permeability tensor,\\
\texttt{kzz} = zz component of permeability tensor,\\
\texttt{kappa\_s} = solid bulk modulus,\\
\texttt{kappa\_f} = fluid bulk modulus,\\
\texttt{kappa\_fr} = frame bulk modulus,\\
\texttt{eta\_f} = fluid viscosity,\\
\texttt{mu\_fr} = frame shear modulus.\\
\end{description}
Using an external mesh (for instance coming from CUBIT/TRELIS), poroelastic materials have the ID number 3, while 1 is acoustic and 2 is elastic (see the example in the package: EXAMPLES/homogeneous\_poroelastic).\\

>>>>

\subsection{PML absorbing boundary layers}
